{\LARGE Model Selection for Scalar-on-Function Regression \\ with Applications to Near-Infrared Spectroscopy}

### 2022-02-02 Paper/main.tex

	 To exploit the regularity of the curves of the spectra, we introduced different basis functions and demonstrated the importance of the truncation parameter $\mathcal{K}$ for the estimation in SECTION HERE. For the simulation study, we rely on the introduced estimation strategies with the introduced basis functions and focus on choosing the truncation parameter $\mathcal{K}$ as well as the number of FPC, which is as well affected by $\mathcal{K}$, by ten fold cross-validation. While cross-validation is common for selecting $\mathcal{K}$, the number of FPC in practice is often truncated after a prespecified amount of explained variability \cite{kokoszka_introduction_2017}, which might not be optimal since FPC with smaller eigenvalues may have greater influence on the prediction \cite{Jolliffe_1982}.

>>>>

	 To exploit the regularity of the curves of the spectra, we introduced different basis functions and demonstrated the importance of the truncation parameter $K$ for the estimation in SECTION HERE. For the simulation study, we rely on the introduced estimation strategies with the introduced basis functions and focus on choosing the truncation parameter $K$ as well as the number of FPC, which is as well affected by $K$, by ten fold cross-validation. While cross-validation is common for selecting $K$, the number of FPC in practice is often truncated after a pre specified amount of explained variability \cite{kokoszka_introduction_2017}, which might not be optimal since FPC with smaller eigenvalues may have greater influence on the prediction (c.f \cite{Jolliffe_1982}). This might apply for this simulation as well, since certain eigenfunctions could be resulting from certain chemical combinations and overtones in the absorption bands of the spectra, that could have high predictive power, but explain only little variability of the spectra (SEE APPENDIX
